The SMT Competition 2015--2018

### 2018-10-22 2018/report/SMT-COMP.tex
affiliation, fixes

\author{%
  \name{Tjark Weber (competition chair, 2015--2018)}
  \email{tjark.weber@it.uu.se} \\
  \addr Uppsala University \\
  Uppsala \\
  Sweden
  \AND
  \name{Sylvain Conchon (co-organizer, 2015--2016)}
  \email{Sylvain.Conchon@lri.fr} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
  \email{david@dimap.ufrn.br} \\
  \addr Federal University of Rio Grande do Norte \\
  Natal \\
  Brazil
  \AND
  \name{Matthias Heizmann (co-organizer, 2016--2018)}
  \email{heizmann@informatik.uni-freiburg.de} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Aina Niemetz (co-organizer, 2018)}
  \email{niemetz@cs.stanford.edu} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Giles Reger (co-organizer, 2017--2018)}
  \email{giles.reger@manchester.ac.uk} \\
  \addr Affiliation \\
  City \\
  Country}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{13cm}|} %TODO: fix width
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC [\TODO]       & Valera Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo          & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE            & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector         & Mathias Preiner
                        (Johannes Kepler University)\\
    COLIBRI           & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo         & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3              & Kshitij Bansal
                        (New York University)\\
    CVC4              & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2          & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB              & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT             & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog            & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT           & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol       & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT        & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP               & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt            & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire           & Giles Reger
                        (University of Manchester)\\
    veriT             & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat              & Martin Velez
                        (University of California, Davis)\\
    Yices2            & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3                & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

@@

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven Kurt G\"odel medals.  The competition
organizers awarded these to the following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide ranking (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0).
\end{itemize}

>>>>

\author{%
  \name{Tjark Weber (competition chair, 2015--2018)}
  \email{tjark.weber@it.uu.se} \\
  \addr Uppsala University \\
  Uppsala \\
  Sweden
  \AND
  \name{Sylvain Conchon (co-organizer, 2015--2016)}
  \email{Sylvain.Conchon@lri.fr} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{David D\'{e}harbe (co-organizer, 2015--2016)}
  \email{david@dimap.ufrn.br} \\
  \addr Federal University of Rio Grande do Norte \\
  Natal \\
  Brazil
  \AND
  \name{Matthias Heizmann (co-organizer, 2016--2018)}
  \email{heizmann@informatik.uni-freiburg.de} \\
  \addr Affiliation \\
  City \\
  Country
  \AND
  \name{Aina Niemetz (co-organizer, 2018)}
  \email{niemetz@cs.stanford.edu} \\
  \addr Stanford University\\
  Stanford \\
  USA
  \AND
  \name{Giles Reger (co-organizer, 2017--2018)}
  \email{giles.reger@manchester.ac.uk} \\
  \addr Affiliation \\
  City \\
  Country}

@@

\begin{table}
  \caption{Participants (2015--2018)}
  \label{table:participants}
  \centering
  \begin{tabular}{|l|p{13cm}|} %TODO: fix width
    \hline
    Solver & Submitters (Affiliations)\\
    \hline
    ABC [\TODO]       & Valeriy Balabanov
                        (Mentor Graphics)\\
    Alt-Ergo          & Albin Coquereau
                        (CNRS and University of Paris-Sud)\\
    AProVE            & Carsten Fuhs
                        (University College London; Birkbeck, University of London)\\
    Boolector         & Mathias Preiner
                        (Johannes Kepler University)\\
    COLIBRI           & Fran\c{c}ois Bobot
                        (French Alternative Energies and Atomic Energy Commission)\\
    Ctrl-Ergo         & Mohamed Iguernlala
                        (CNRS and University of Paris-Sud)\\
    CVC3              & Kshitij Bansal
                        (New York University)\\
    CVC4              & Kshitij Bansal, Clark Barrett, Andres N\"otzli, Duligur Ibeling
                        (New York University; Stanford University)\\
    MapleSTP          & Jimmy Liang
                        (University of Waterloo)\\
    MinkeyRink        & Trevor Hansen
                        (University of Melbourne)\\
    OpenSMT2          & Matteo Marescotti, Antti Hyv\"arinen
                        (University of Lugano)\\
    ProB              & Sebastian Krings
                        (University of D\"usseldorf)\\
    Q3B               & Martin Jon\'a\v{s}
                        (Masaryk University)\\
    raSAT             & Tung Vu Xuan
                        (Japan Advanced Institute of Science and Technology)\\
    Redlog            & Haniel Barbosa
                        (Inria Nancy)\\
    SMT-RAT           & Florian Corzilius, Gereon Kremer
                        (RWTH Aachen University)\\
    SMTInterpol       & J\"urgen Christ
                        (University of Freiburg)\\
    SPASS-SATT        & Martin Bromberger
                        (Max Planck Institute for Informatics)\\
    STP               & Mate Soos, Trevor Hansen, Norbert Manthey
                        (National University of Singapore; University of Melbourne; Amazon Web Services)\\
    toysmt            & Masahiro Sakai
                        (Toshiba Corporation)\\
    Vampire           & Giles Reger
                        (University of Manchester)\\
    veriT             & David D\'eharbe, Haniel Barbosa, Hans-J\"org Schurr
                        (Federal University of Rio Grande do Norte; Inria Nancy)\\
    XSat              & Martin Velez
                        (University of California, Davis)\\
    Yices2            & Bruno Dutertre, Dejan Jovanovi\'c
                        (SRI International)\\
    Z3                & Christoph Wintersteiger, Aleksandar Zelji\'c
                        (Microsoft Research; Uppsala University)\\
    \hline
  \end{tabular}
\end{table}

@@

The 2018 edition of the competition was again part of the FLoC Olympic
Games, which sponsored seven FLoC 2018 medals.  The competition
organizers awarded these to the following solvers:
\begin{itemize}
\item The best three main-track solvers according to the
  competition-wide ranking (first place: CVC4, second place:
  Yices-2.6.0, third place: SMTInterpol);
\item the solver(s) that won the QF\_BV division in the main track
  (sequential ranking: Boolector, parallel ranking: Minkeyrink-MT);
\item the solver that won the most competitive divisions in the
  application track (Yices-2.6.0);
\item the solver that won the most competitive divisions in the
  unsat-core track (Yices-2.6.0).
\end{itemize}
